Towards open collaboration in biomedical and health research: An open collaborative scoping review

### 2025-02-10 doc/paper.qmd
style: :lipstick: use a nicer looking PDF format (#117)
Closes #108

Doesn't need a review.

---
title: "Towards open collaboration in biomedical and health research: An open collaborative scoping review"
date: last-modified
author:
  - name: Mario Garcia
    affiliations:
      - ref: ku
  - name: Daniel B. Ibsen
    affiliations:
      - ref: sdca
      - ref: au
  - name: Luke W. Johnston
    affiliations:
      - ref: sdca
      - ref: au
affiliations:
  - id: sdca
    name: Steno Diabetes Center Aarhus
    country: Denmark
  - id: au
    name: Aarhus University
    country: Denmark
  - id: ku
    name: Copenhagen University
    country: Denmark
format:
  html: default
  typst:
    columns: 2
    papersize: a4
    margin:
      x: 2cm
      y: 2cm
format-links:
  - html
  - format: typst
    text: PDF
    icon: file-pdf
---

>>>>

---
title: "Towards open collaboration in biomedical and health research: An open collaborative scoping review"
date: last-modified
author:
  - name: Mario Garcia
    affiliations:
      - ref: ku
  - name: Daniel B. Ibsen
    affiliations:
      - ref: sdca
      - ref: au
  - name: Luke W. Johnston
    affiliations:
      - ref: sdca
      - ref: au
affiliations:
  - id: sdca
    name: Steno Diabetes Center Aarhus
    country: Denmark
  - id: au
    name: Aarhus University
    country: Denmark
  - id: ku
    name: Copenhagen University
    country: Denmark
format:
  html: default
  academic-typst:
    section-numbering: "1.1.1"
    columns: 2
    papersize: a4
    margin:
      x: 2cm
      y: 2cm
format-links:
  - html
  - format: academic-typst
    text: PDF
    icon: file-pdf
abstract: |
  {{< lipsum 1 >}}
execute: 
  echo: false
  message: false
  warning: false
---
